Ultrafast Electron Microscopes: Design Criteria, Electron Sources, and Column Modeling

### 2013-04-06 inc/model_results/spacecharge/spacecharge.tex
merging more comments into spacecharge results

The expected trend is evident in \ref{fig:spacecharge_noacc} which presents the predicted HW1/eM pulse width $\sqrt{2 \sigma_{\smallT}}$ (solid line) and longitudinal length $\sqrt{2 \sigma_{z}}$ (dashed line) after a propagation distance of 15cm as a function of the number of electrons in the pulse.
Once again, this simulation employs the idealistic pulse described earlier, starting with a velocity of $c/3$ where $c$ is the speed of light in a vacuum (1.5ns total propagation time), initial width of 1 mm, HW1/eM pulse duration 1 ps, and an excess photoemission energy $\Delta E = $ 0.5 eV.
For these conditions, used to isolate the behavior of a propagating pulse from its creation environment, the simulations clearly indicate that both the electron beam width and length at the end of the simulation will remain unchanged below about $10^5$ electrons/pulse; that is, global space-charge effects only significantly influence the pulse propagation for pulses having more than $10^5$ electrons/pulse.
In the absence of space-charge effects, the presented oblate shaped pulses should be maintained as such during unforced propagation because the initial values of the electron pulse' divergence and temporal broadening rate are both proportional to $\Delta E^{1/2}$ but not to $N$.

@@

Consider now a simulation comparable to the one presented above, but which uses the realistic initial conditions set.
The pulse is generated by a 1 mm width 1 ps laser (HW1/eM) and accelerated by an electron gun which is 20mm in length and which accelerates the pulse through a voltage of 30 kV to speed $c/3$, the same velocity as in the idealistic case.
The results of this simulation are presented in \ref{fig:spacecharge_acc}.
It is immediately obvious that the final transverse width is larger than in the ideal case presented in \ref{fig:spacecharge_noacc}, even in the low charge-density regime; this is primarily due to the additional divergence imparted by the negative lensing at the anode (see Section \ref{sec:gun_model}).
One can see that though the pulse size does increase beyond a certain total pulse charge, and while that trend appears to start at a higher charge, due to the complexity of the pulse dynamics it is rather difficult to compare the exact charge-density from this plot to that in the idealistic case.
What can be seen is that the transverse size increases more sharply with pulse charge at higher levels.
Since the pulse is already diverging in the transverse direction, this is compounded by the increased pulse charge.
This divergence then acts to lower the overall charge-density more quickly, thus the longitudinal pulse length is not affected as strongly as was seen in \ref{fig:spacecharge_noacc}.

>>>>

The expected trend is evident in \ref{fig:spacecharge_noacc} which presents the predicted HW1/eM pulse width $\sqrt{2 \sigma_{\smallT}}$ (solid line) and longitudinal length $\sqrt{2 \sigma_{z}}$ (dashed line) after a propagation distance of 15cm as a function of the number of electrons in the pulse.
Once again, this simulation employs the idealistic pulse described earlier, starting with a velocity of $c/3$ where $c$ is the speed of light in a vacuum (1.5ns total propagation time), initial width $w_{\smallT} = $ 1 mm, HW1/eM pulse duration 1 ps ($w_{z} = $ 0.1 mm), and an excess photoemission energy $\Delta E = $ 0.5 eV.
For these conditions, that are used to isolate the behavior of a propagating pulse from its creation environment, the simulations clearly indicate that both the electron beam width and length at the end of the simulation will remain unchanged below about $10^5$ electrons/pulse; that is, global space-charge effects only significantly influence the pulse propagation for pulses having more than $10^5$ electrons/pulse.
In the absence of space-charge effects, the presented oblate shaped pulses should be maintained as such during free-space propagation, because the initial values of the electron pulse's divergence and temporal broadening rate are both proportional to $\Delta E^{1/2}$ but not to $N$.

@@

Consider now a simulation comparable to the one presented above, but which uses the realistic initial conditions set (\ref{eq:summary}).
The pulse is generated by a 1 mm width 1 ps laser (HW1/eM) and accelerated by an electron gun which is 20mm in length and which accelerates the pulse through a voltage of 30 kV to speed $c/3$, the same velocity as in the idealistic case.
The results of this simulation are presented in \ref{fig:spacecharge_acc}.
It is immediately obvious that the final transverse width is larger than in the ideal case presented in \ref{fig:spacecharge_noacc}, even in the low charge-density regime; this is primarily due to the additional divergence imparted by the negative lensing at the anode (see Section \ref{sec:gun_model}).
One can see that though the pulse size does increase beyond a certain total pulse charge, and while that trend appears to start at a higher charge, due to the complexity of the pulse dynamics it is rather difficult to compare the exact charge-density from this plot to that in the idealistic case.
What can be seen is that the transverse size increases more sharply with pulse charge at higher levels.
Since the pulse is already diverging in the transverse direction, this is compounded by the increased pulse charge.
This divergence then acts to lower the overall charge-density more quickly, thus the longitudinal pulse length is not affected as strongly as was seen in \ref{fig:spacecharge_noacc}.
